---
title: "Assignment"
author: "Sanjay S"
date: "2022-09-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1 What happens if you make a scatterplot of class versus drv? Why is the plot not    useful?
Ans:The class and drv attributes are categorical. Therefore the plot shows the mapping between these categories.
```{r}
library(tidyverse)
ggplot(mpg,aes(x=class,y=drv))+
  geom_point()
```
2 What’s gone wrong with this code? Why are the points not blue?
  ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
  
  Ans:The points are not blue because aesthatic have two parameter so the color parameter is not accept ,so the color parameter should be in outsaid the aesthatic function.

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```
3 a)	What happens if you map a aesthetic to something other than a variable           name, like aes(colour = displ < 5)?
```{r}
library(tidyverse)
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, colour = displ < 5))
```
  b) b)	What does the stroke aesthetic do? What shapes does it work with?
  Ans:The stroke aesthetic  to adjust the object thickness for shapes.
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy), stroke=3)
```
4 Read? Facet_wrap. What does nrow do? What does ncol do? What other options         control the layout of the individual panels? Why doesn’t facet_grid() have      nrow and ncol variables?

Ans:Facet grids do not have these configuration because the rows and cols are determined by the specified attributes.
```{r}
?facet_wrap  
```
5 a) a)	What plots does the following code make? What does . do? 

Ans:facet_grid() divides the plot in the particular area. That is used to make the plot into subplot.
 
  
  ggplot(data = mpg) + 
geom_point(mapping = aes(x = displ, y = hwy)) +
facet_grid(. ~ cyl)                                                                          

```{r}
 ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)
```
```{r}
 ggplot(data = mpg) + 
geom_point(mapping = aes(x = displ, y = hwy)) +
facet_grid(. ~ cyl)
```

 b) b)	When using facet_grid() you should usually put the variable with more            unique levels in the columns. Why? 
 
  Ans:becasue it  gives meaningful interpretation.
  
6) What geom would you use to draw a line chart? A boxplot? A histogram? An area     chart?   
Ans:
        line chart: geom_line()
        box plot: geom_boxplot()
        histogram: geom_histogram()
        area chart: geom_area()
```{r}
ggplot(data=mpg)+
  geom_boxplot(aes(x=displ,y=hwy))

ggplot(data=mpg)+
  geom_line(aes(x=displ,y=hwy))


ggplot(data=mpg)+
  geom_area(aes(x=displ,y=hwy))
```
7) Will these two graphs look different? Why/why not?

Ans:No , the two graphs looks similar.Becasue both geom_point() and geom_smooth() use same          data and mappings



```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
     geom_point() +
     geom_smooth()
```
```{r}
ggplot() +
     geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) +
     geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))
```

8) What does geom_col() do? How is different to geom_bar()?
 Ans: geom_col() requires both x and y where as geom_bar() requires only x variables.
```{r}
ggplot(data = mpg) +
     geom_col( mapping = aes(x = displ, y = hwy))
```


```{r}
ggplot(data = mpg) +
     geom_bar( mapping = aes(x =class))
```
9) What is the default geom associated with stat_summary()? How could you rewrite the previous plot to use that geom function instead of the stat function?
Ans:The geom_pointrange is a default geom associate with stat_summary()
```{r}
ggplot(data = diamonds) +
  geom_pointrange(mapping = aes(x = cut, y = depth),
                 stat="summary", 
               fun.ymin = min,
               fun.ymax = max,
               fun.y = mean)
```
10 What does the plot below tell you about the relationship between city and highway mpg? Why is coord_fixed() important? What does geom_abline() do?

Ans:When city mileage increases hwy mileage also increases. There is a positive relationship between city mileage        and hwy mileage.
      coord_fixed: Adjust the values in the data set.
      geom_abline: Its shows the prediction or regression between x and y.
```{r}
ggplot(data = mpg, mapping =aes(x =cty, y =hwy)) +
geom_point() +
geom_abline() +
coord_fixed()
```

